RSA Project Report Paper

### 2016-11-29 Paper/Paper.tex
Merge ours

\section{Introduction}
For this assignment, we were given the task of breaking RSA encryption. The data we were given is simply the public key, and the cipher modulus. The problem has specified that the message was encrypted to number format by each being equal to a set of one or two number (Ex: A = 1,B = 2,with Z = 26).

@@

\indent This is all the information afforded to us to solve the problem of recovering the message. Now we will discuss potential attacks against RSA and the pitfalls of many of them given the information provided.

In this paper, we will assume Alice is the message sender and Bob is the message receiver who receives messages from Alice. Eve is the malicious devil attacker to try to intercept and decrypt the message. And d represents the private key.

@@

\subsubsection{Partial Key Exposure}
A partial key exposure attack involves a situation where if an attacker can expose around a quarter of the bits of the private key, he can construct the rest of d providing the public exponent is small (small meaning $e <\sqrt[]{N}$ where N and e are the public RSA key). This attack was developed when the above statement was discovered by Boneh,Durfee and Frankel. There is involved in this attack which I will outline below (quoted from "20 years \dots RSA" [4].)
\\\\
\textbf{Theorem (BDF): }\textit{Let (N,d) be an RSA private key in which N is n bits long. Given the $\left\lceil n/4 \right\rceil$ least significant bits of d. Marvin can reconstruct d in time linear in $elog_2e$}
\\\\
The proof of this relies on a second theorem from Coppersmith which we will not be outlining at this time. This attack is actually interesting do to a statement that it may be possible to get the RSA system to leak a portion of the significant bits of the private key and with a few equations be able to approximate the private key. We ultimately did not pursue this line of attack due to fears of spending too much time on a potentially fruitless line of attack.

\subsection{implementation attacks}
The implementation attacks involve attacks against applications of RSA rather than the RSA mechanism itself. These
attacks involve timing attacks, attacks involving computer glitches and one involving the an RSA message padded using
the public key cryptography standard 1. These attacks are incompatible with our problem to a much higher degree than
the other attacks so we won't go into to details about them.
\section{Factoring Attacks Against RSA}
\subsection{Special Factoring Methods}
		The efficiency of this type of methods usually depends on the size of the first prime factor or some special form of N. If the first prime factor is small (N is less than 100 bits) or N can be expressed in some special forms, these methods can find the first prime factor fast.
		Thus, we usually apply these special factoring methods to find whether there is a small prime factor to divide N so that we can decrease the size of N before proceed with the general factoring methods.

 \subsubsection{ Brute Force}
		The brute force method we used here is to do the trial division from 2 and 3 to $\sqrt{N}$ and increase by 2.
		In this month, we search up to 58248674129 (35-bit), which is 21 digits difference with the second prime factor 64820903298591432157114065708311(105-bit).
		And it will take us 7.6*$10^{18}$ years to reach the second prime factor if we use brute force search. (all the calculations above are done by Java) 
		Therefore, if we only use brute force search to factor N, we won't be able to reach the solution until 7.6*$10^{16}$ generations after (and each generation should continue this task non-stop).

@@

		In our case, we factor 495960937377360604920383605744987602701101399399359259262820\\733407167 = 809*613054310726032886180943888436325837702226698886723435429939101863 using Pollard's rho algorithm within 6 ms by Java.
		And after using Miller-Rabin's primality test, we found that 613054310726032886180943888436325837702226698886723435429939101863 is a composite number.
		So, we keep factoring 61305431072603288618094388843632583770222669888\\672435429939101863 using Pollard's rho algorithm.
		However, the Pollard's rho algorithm program is still running, so we failed to use this algorithm to factor N in one month.
\subsubsection{Pollard's P-1}
By Fermat’s Little Theorem, if $a$ and $p$ are coprime, then $a^{p-1} = 1(mod\ p)$, which means that $a^{k(p-1)} (mod\ p)$ should also be $1$. Say $p$ and $q$ are prime factors of the number we want to factor, $N$. If we can find an integer $L$, such that $p-1| L$, meaning $k(p-1) = L$ for some integer $k$ and $a^{L} = 1(mod p)$, we then know that $p|a^{L-1}$. From there we can calculate gcd($a^{L-1}$, $N$), which we can have two cases. The first case is if the gcd($a^{L-1}$, $N$) is not equal to $N$, which means that the gcd must be our prime factor p (since $a^{L-1} = kp$, for some integer $k$, $N = pq$, and gcd($kp$, $pq$) = $p$). The second case is if gcd($a^{L-1}$, $N$) = $N$, which implies that $N| a^{L-1}$. In this case $q$ will also divide $a^{L-1}$, meaning $a^{L} = 1(mod q)$ (because $a^{L-1} = 0(mod q)$).
\\\\Algorithm
	\\1. Choose $a$, where $1<a<n$
	\\2. Check if gcd($a$,$n$) != 1, if it is, (though not likely), then you’ve found a factor, $a$.
	\\3. Otherwise, for $r$ = $2,3,..$ compute the gcd($a^{r!-1}$, $n$) = $d$:
	\\If $d = n$, then go back to (1), try a different a
	\\If $d \ne n$, but $d > 1$,  then $d$ is a prime factor of 
	\\Otherwise, if $d = 1$, increment $r$ and repeat
\\\\
Note: We use $r!$ as our exponent since $r!$ will have a lot of small prime factors, but we can also have a bound $B$, and take the product of all primes < $B$ as well, with an increasing $B$ instead of $r!$. The goal is to find an $L$ such that it is a large multiple of $p-1$
\\\\An attempt at factoring our $N$ using Pollard’s $p-1$ factoring algorithm also proved to yield similar results with Pollard rho factorization. The algorithm itself, which relies on $p-1$, where $p$ is a prime factor of $N$ containing a lot of small prime factors, fails to further factor $N$ beyond the initial 809 factor.

@@

\section{The Quadratic Sieve}
At last we come to the crux of our assignment, The Quadratic Sieve. The quadratic sieve is faster for numbers under 100 digits\cite{pomerance}. This method was invented by Carl Pomerance in 1981 after a series of enhancements on Fermat's factoring method led to the idea of utilizing smooth numbers to set up a matrix to with enough vectors of which to assure that the squares need for Fermat's method would be found. We decided within the first two weeks to stick to the Quadratic Sieve over other methods after we exhausted all the other options listed above.
\\\\
Firstly we will discuss the Quadratic Sieve in detail, explaining what the algorithm is and how it works (similar to the above sections but tackling it in depth). Then we will explain our journey through the implementation of the Quadratic Sieve, our problems as well as the solutions to those problems. Then we will finally discuss the final results to this assignment.
\subsection{Basic's of the Algorithm}

@@

\subsubsection {Kraitchik's Factorization}
Kraitchik's method is instead of checking $x^2-n$ is a square, he suggests to check $x^2 - kn$ a square number, which is equivalent to find $y^2 \equiv x^2 \pmod{n} $. And the only interesting solution is $ x \not\equiv \pm y \pmod{n}$. Besides this, instead of seeking one $x^2-n$ is square, he was looking for a set of number $ \{x_1, x_2, \dots, x_k\} $ such that $\displaystyle y^2 \equiv \prod_{i=1}^k{(x_i^2 - n)} \equiv \prod_{i=1}^k{x_i^2} \equiv \left (\prod_{i=1}^k{x_i}\right)^2 \pmod{n} $ is square. if he can find a relation like this, then, the factors of n is $\displaystyle gcd(|y \pm \prod_{i=1}^k{x_i}|, n)$

\subsubsection {Dixon's Factorization}
One of the great improvement of Dixon's method compared to the previous methods is that he replaces the requirement from ``is a square of an integer'' to ``has only small prime factors''. To explain this, we need introduce two concepts which are \textbf{Factor Base} and \textbf{Smooth Number}.

\textbf{Factor Base} is a set of prime factors $S_{fb}=\{p | p \le B\}$ where $B$ is some integer.

\textbf{Smooth Number} is an integer in which all its prime factors are within the \textbf{Factor Base} which means if we choose integer $B$ and $Q$, $Q = \prod_{i=1}^k{p_i^{a_i}}$ where $a_i, k \in \mathbb{Z}, p_i \in S_{fb}$. We called Q is a \textbf{B-Smooth} Number.

Recall Kraitchik's Method, he suggests to find a relation $y^2 \equiv \left (\prod_{i=1}^k{x_i}\right)^2 \pmod{n}$. But Dixon's idea is different, he is looking for the relation of $\displaystyle y^2 \equiv Q \equiv \prod_{i=1}^k{p_i^{a_i}} \pmod{n}$ where $a_i \in \mathbb{Z},\ k=|S_{fb}|,\ p_i \in S_{fb}$. For each relation  found, it can be represented as an exponent vector $\vec{v} = \{a_1, a_2, \dots, a_k\}$ over $\mathbb{F}_{2}$, and after finding $k$ relations, we have a matrix $m = \{\vec{v_i} | i \le k\}$. And searching the null space of this matrix could help us to find the square integer. Since $M\vec{v} = \vec{0}$ where $\vec{v} \in Null\ Space$, we know which rows sum together are equal to $\vec{0}$, which also implies the products of corresponding Q to that row is a square integer. After we find the relations, let $x^2 = \prod_i^k{Q_i}$, the factor of n is $gcd(y\pm x, n)$

\subsection {Math and Algorithm in Quadratic Sieve}
Once again, like in previous factoring methods such as in Fermat’s or Dixon’s, we rely on finding two integers, $x$ and $y$,such that N can be expressed as the difference of two squares, $x^{2}-y^{2}$. From there we can apply simply algebra find the two factors of $N$, $(x-y)$ and $(x+y)$. This may seem simply enough, but how exactly do you find such $x$ and $y$? Surely we could try to check every integer $x$, from $sqrt{N}$ to $N$ and see if $x^{2}-N$ is a square or not, like in Fermat’s, but this method is too slow for large numbers of $N$. For small numbers of $N$, trial division would work fine. We, however, don’t need to search the entire interval to find a square. Take for example the number $N = 1649$. The
 $\sqrt{1649} = 41$ so we can begin being to find squares starting with 41.  We have\\
 $41^{2} = 32 = 2^{5}$ \\ $42^{2} = 115 = 5\cdot 23$ \\ $42^{3} = 200 = 2^{3}\cdot 5^{2}$ mod $N$, and so on.

@@

So instead of searching through the entire interval from $sqrt{N}$ to N looking for an individual integer a, such that $a^{2} - N = b^{2}$, we can find a subsequence of integers, such that the product will yield a square as well. But how exactly do you find such a subsequence? Surely we cannot examine all subsequences, for given an interval of length L, there would be $2^{L}$ possible subsequences, in other words, an exponential growth in the number of subsequences as L gets bigger. Furthermore, how long of a sequence do we need to examine before we find such a subsequence, and how do we know what the subsequence is? 

@@

\\\\LEMMA. If $m_1$,$m_2$,...$m_k$ are positive B-smooth integers, and if $k > \pi(B)$ (where $\pi{B})$ denotes the number of primes in the interval $[1, B]$, then some non-empty subsequence of ($m_i$) has a product of a square. (Pomerance)

@@

\\Essentially, Pomerance’s lemma states that if we were to find at least $\pi{B}$ B-smooth numbers, we are able to find some subsequence of those numbers that would be a product of a square. So say we have a sequence of numbers $m_1$,$m_2$,...$m_k$, where $k>\pi{B}$, we can represent each $m_i$ as a product of those primes less than $B$, namely $p_1$,$p_2$,...$p_j$. From here we are only interesting in a subsequence of $m_i$’s where there product is a square, but how do we go about finding it? Well, by applying some linear algebra, we can represent each number as an exponent vector of length $j$, the length of our factor base, where each entry in the vector corresponds to the exponent corresponding to the same prime in the prime factorization of $m_i$.For example, given a factor base of \{2,3,5,7\}, the exponent vector of the number 336 would just be [4, 1, 0, 1]. 
\\\\ Additionally, we want to work with numbers in GF(2), since we are only interested whether or not some combination will yield even exponents, represented as 0 for even exponent and 1 for odd exponent in our vector, because ultimately we want some subsequence whose product is a square, which means each exponent will be a multiple of 2. After creating such a $k$ by $j$ matrix, we want to find some number of rows who when combined together form a vector of 0's, the zero vector of length $j$, which is why we need to calculate the null space of the matrix. Put simply, the null space of a matrix is the set of all vectors, $v$, such that given a matrix $A$, the product $A\cdot v$, yields the zero vector, which is exactly what we want. In our case the null space will yield vectors, each vector containing only entries of 1s and 0s, in which every 1 corresponds to a row in which that $m_i$ belongs to our subsequence. 
\\\\Another problem that arises, however, is selecting such a bound B. What exactly is a good limit for the bound B? 
\\How do we populate the factor base given a bound B? Perhaps it may seem necessary to store a large number of primes in order to sieve, but in fact we can easily generate all primes less than B through applying the Sieve of Eratosthenes:

@@

\\2. Find the next number in the table after p that is not yet crossed off and set p to that number; and then repeat from step 1. (O’Niel)
\\\\Now, the problem is, how do we find the necessary amount of B-smooth numbers needed to factor N? Surely, a naive approach would be to trial divide a number by the primes in the factor base until you either get a 1, in which case the number is B-smooth, or you get a number larger larger than B which is not a multiple of any prime in the factor base, in which case it’s not B-smooth. Indeed, this approach would be much too slow, given a sufficiently large bound B, B-smooth numbers are far and few between. It would be a huge waste of time and resources. 
\\A further improvement could be to only consider numbers which are multiples of primes in the factor base. Say in our interval $[\sqrt{N},N]$ and a prime in our factor base, p, we notice that at some point, x, the number $x^{2}-N$ will be a multiple of p, which can be represented as $\sqrt{N}+i$, where i is the distance from the start of the interval. From there, every subsequent multiple of p is $k*i$ distance away from $\sqrt{N}$. Essentially we will have to solve for $x$ in $x^{2}-N\equiv 0(mod p_i)$, which can yield either 2, 1 or 0 solutions. We can do this for every $p_i$ in the factor base and ‘mark’ numbers that are multiples of said prime. Then, we will only check marked numbers in our interval by dividing only those primes that marked the number, hence not having to check every number in the interval, and not having to trial divide by every prime in the factor base. In the end, this method will work, but does not scale well (as in our case), which is further explained in Sect. 4.5.

@@

Additionally, with a defined bound B, should we consider all the primes less than B? Recall the definition of a quadratic residue:

@@

\\Now the obvious question arises: how do you know if N is a quadratic residue modulo p? Recall the definition of the legendre symbol:

@@

$\frac{a}{p} = $
\\$1$ if a is a quadratic residue modulo p and $a\not\equiv 0(mod p)$
\\$-1$ if a is quadratic non-residue modulo p
\\$0$ if $a\equiv 0(mod p)$
\\\\Additionally we will introduce the Law of Quadratic Reciprocity:
Definition: If p and q are distinct odd primes then:
\\(a)$(\frac{p}{q})(\frac{q}{p}) = (-1)^{\frac{(p-1)(q-1)}{4}}$
\\(b)$\frac{1}{p} = 1$
\\(c)$(\frac{-1}{p}) = (-1)^{\frac{p-1}{2}}$
\\(d)$(\frac{2}{p} = (-1)^{\frac{p^{2}-1}{8}})$

@@

From now, we know two ways to test whether $n$ is a quadratic residue mod p, one is Euler Criterion, and the other is Legendre symbol. In practice, probably because we factor base is not insanely large, we did not noticed how much faster does Legendre symbol than the Euler criterion (since Euler criterion is an $\mathcal{O}(\log{n}) $ algorithm).

\subsubsection{Shanks Tonelli's Algorithm}

Shanks Tonelli's Algorithm is a faster algorithm to find the root of a quadratic residue. In class, we only learn the simple case, which is when $p \equiv 3 \pmod{4}$. Since this algorithm is very important for quadratic sieve, we are going to prove the algorithm.

@@

let $p-1 = 2^eS,\ x \equiv n^{\frac{S+1}{2}} \pmod{p},\ t \equiv n^S \pmod{p}.$

we have, $x^2 \equiv n^{S+1} \equiv n^Sn \equiv tn \pmod{p}$, notice that,

@@

if $t \not\equiv 1 \pmod{p}$, then find a quadratic non-residue $a$ and let $b \equiv a^S \pmod{p}$, then, $b^{2^e} \equiv (a^S)^{2^e} \equiv a^{2^eS} \equiv a^{p-1} \equiv 1 \pmod{p}$, Since we know $a$ is a quadratic non-residue, By Euler Criterion, $a^{\frac{p-1}{2}} \equiv b^{2^{e-1}} \equiv -1 \pmod{p} \rightarrow 2^e$ is the order of b.

we have $t^{2^e} \equiv 1 \pmod{p}$, and we let $2^{e^\prime}$ be the order of $t \pmod{p}$, since $n$ is a quadratic residue, $e^\prime \le e-1$

let $c \equiv b^{2^{e-e^\prime-1}} \pmod{p}$, $b^\prime \equiv c^2$, $t^\prime = tb^\prime$, $x^\prime = cx$, after this construction, $x^{\prime 2} \equiv t^\prime n \pmod{p}$ still holds, since $x^{\prime 2} \equiv b^{2^{e-e^\prime}}x^2 \equiv tnb^{2^{e-e^\prime}} \equiv tnb^\prime \equiv  t^\prime n \pmod{p}$. And we can repeat this process until $e^\prime = 0$ we can find a $t^\prime = 1$, and our final solution is $ \pm x^\prime \pmod{p}$

@@

>>>>

	\section{Introduction}
	For this assignment, we were given the task of breaking RSA encryption. The data we were given is simply the public key, and the cipher modulus. The problem has specified that the message was initially encoded to a number, where each letter corresponds to an integer from 1 to 26 (Ex: A = 1,B = 2,... Z = 26).

@@

	\indent This is all the information afforded to us to solve the problem of recovering the original message. Now we will discuss potential attacks against RSA, their pros/cons, and whether or not we can actually use such attacks with the given information provided.

@@

	\subsubsection{Partial Key Exposure}
	A partial key exposure attack involves a situation where if an attacker can expose around a quarter of the bits of the private key, he can construct the rest of d providing the public exponent is small (small meaning $e <\sqrt[]{N}$ where N and e are the public RSA key). This attack was developed when the above statement was discovered by Boneh,Durfee and Frankel. There is involved in this attack which I will outline below (quoted from "20 years \dots RSA" [4].)
	\\\\
	\textbf{Theorem (BDF): }\textit{Let (N,d) be an RSA private key in which N is n bits long. Given the $\left\lceil n/4 \right\rceil$ least significant bits of d. Marvin can reconstruct d in time linear in $elog_2e$}
	\\\\
	The proof of this relies on a second theorem from Coppersmith which we will not be outlining in this paper. This attack is actually interesting to implement due to the statement that it may be possible to get the RSA system to leak a portion of the significant bits of the private key and with a few equations be able to approximate the private key. We ultimately did not pursue this line of attack due to fears of spending too much time on a potentially fruitless line of attack.

	\subsection{Implementation Attacks}
	The implementation attacks involve attacks against applications of RSA rather than the RSA mechanism itself. These
	attacks involve timing attacks, attacks involving computer glitches and one involving the an RSA message padded using
	the public key cryptography standard 1. These attacks are incompatible with our problem to a much higher degree than
	the other attacks so we won't go into to details about them.
	\section{Factoring Attacks Against RSA}
	\subsection{Special-Purpose Factoring Methods}
	The efficiency of this type of methods usually depends on the size of the first prime factor or some special form of N. If the first prime factor is small (N is less than 100 bits) or N can be expressed in some special forms, these methods can find the first prime factor fairly quickly.
	Thus, we usually apply these special factoring methods to quickly discover whether there is a small prime factor or not, which we can then divide N by, so that we can decrease the size of N(though not by much) before proceeding with the general factoring methods.

	\subsubsection{ Brute Force}
	The brute force method we used here is to do the trial division from 2 and 3 to $\sqrt{N}$ and increasing by 2.
	In this month, we searched up to 58248674129 (35-bit), which is a 21 digits difference from the second prime factor 64820903298591432157114065708311(105-bit) which we found later on using Quadratic Sieving.
	And it will take us 7.6*$10^{18}$ years to reach the second prime factor if we use brute force search. (all the calculations above are done by Java) 
	Therefore, if we only use brute force search to factor N, we won't be able to reach the solution until 7.6*$10^{16}$ generations after (and each generation should continue this task non-stop).

@@

	In our case, we factor 495960937377360604920383605744987602701101399399359259262820\\733407167 = 809*613054310726032886180943888436325837702226698886723435429939101863 using Pollard's rho algorithm within 6 ms by Java.
	And after using Miller-Rabin's primality test, we found that 613054310726032886180943888436325837702226698886723435429939101863 is a composite number.
	So, we keep factoring 61305431072603288618094388843632583770222669888\\672435429939101863 using Pollard's rho algorithm.
	However, the Pollard's rho algorithm program is still running, so we failed to use this algorithm to factor N in one month.
	\subsubsection{Pollard's P-1}
	By Fermat’s Little Theorem, if $a$ and $p$ are coprime, then $a^{p-1} = 1(mod\ p)$, which means that $a^{k(p-1)} (mod\ p)$ should also be $1$. Say $p$ and $q$ are prime factors of the number we want to factor, $N$. If we can find an integer $L$, such that $p-1| L$, meaning $k(p-1) = L$ for some integer $k$ and $a^{L} = 1(mod p)$, we then know that $p|a^{L}-1$. From there we can calculate gcd($a^{L}-1$, $N$), which we can have two cases. The first case is if the gcd($a^{L}-1$, $N$) is not equal to $N$ or $1$, which means that the gcd must be our prime factor p (since $a^{L}-1 = kp$, for some integer $k$, $N = pq$, and gcd($kp$, $pq$) = $p$). The second case is if gcd($a^{L}-1$, $N$) = $N$, which is uninteresting, in which case we should try a different a.
	\\In other words, since we do obviously do not know p, we cannot calculate $a^{p-1}-1$ explicitly so we try instead a multiple of (p-1), say m = k(p-1). The idea is that we do not need to exponentiate exactly up to $p-1$, but a smaller exponent, $k(p-1)$ instead. We need to choose an integer for m such that we get a factor of $n$ if $p-1|m$. By choosing m to be a product of many small primes, the chances that this condition holds will increase.\cite{charest}
	\\\\Algorithm 
	\\1. Choose $a$, where $1<a<n$
	\\2. Check if gcd($a$,$n$) != 1, if it is, (though not likely), then you’ve found a factor, $a$.
	\\3. Otherwise, for $r$ = $2,3,..$ compute the gcd($a^{r!-1}$, $n$) = $d$:
	\\If $d = n$, then go back to (1), try a different a
	\\If $d \ne n$, but $d > 1$,  then $d$ is a prime factor of 
	\\Otherwise, if $d = 1$, increment $r$ and repeat
	\\\\
	Note: We use $r!$ as our exponent since $r!$ will have a lot of small prime factors, but we can also have a bound $B$ as in other implementations \cite{charest} and take the product of primes, $p_i^{\frac{log B}{logp_i}}$ less than $B$ as well, with an increasing $B$ instead of an increasing $r!$. Again, the goal is to ultimately find some exponent, $L$, such that $p|a^{L}-1$ in which the gcd($a^{L}-1$,$N$) = d where $1\le d\le N$.
	\\\\An attempt at factoring our $N$ using Pollard’s $p-1$ factoring algorithm also proved to yield similar results with Pollard rho factorization. The algorithm itself, which relies on $p-1$, where $p$ is a prime factor of $N$ containing a lot of small prime factors, fails to further factor $N$ beyond the initial 809 factor.

@@

	\section{The Quadratic Sieve}
	At last, we had reached the conclusion that we may have to implement the Quadratic Sieve in order to factor our N. According to Carl Pomerance, the mind behind the Quadratic Sieve, the Quadratic Sieve is the fastest for numbers under 100 digits\cite{pomerance}. This method was created after a series of enhancements on Fermat's factoring method utilizing smooth numbers, and matrices of exponent vectors in order to assure that such a square needed for Fermat's method would be found. We decided within the first two weeks to stick to the Quadratic Sieve over other methods after we exhausted all the other options listed above.
	\\\\
	Firstly we will discuss the Quadratic Sieve in detail, explaining what the algorithm is and how it works. We will then explain our our task of implementing the Quadratic Sieve, as well as the problems that we were faced with.
	\subsection{Basic's of the Algorithm}

@@

	\subsubsection {Kraitchik's Factorization}
	Kraitchik's method is to instead of checking whether or not $x^2-n$ is a square, we check whether or not $x^2 - kn$ is a square number, which is equivalent to find $y^2 \equiv x^2 \pmod{n} $. And the only interesting solution is $ x \not\equiv \pm y \pmod{n}$. Besides this, instead of seeking one $x^2-n$ is square, he was looking for a set of number $ \{x_1, x_2, \dots, x_k\} $ such that $\displaystyle y^2 \equiv \prod_{i=1}^k{(x_i^2 - n)} \equiv \prod_{i=1}^k{x_i^2} \equiv \left (\prod_{i=1}^k{x_i}\right)^2 \pmod{n} $ is square. If he can find a relation like this, then, the factors of n is just $\displaystyle gcd(|y \pm \prod_{i=1}^k{x_i}|, n)$

	\subsubsection {Dixon's Factorization}
	One of the greater improvements found in Dixon's method compared to the previous methods is that he replaces the requirement from ``is a square of an integer'' to ``has only small prime factors''. To explain this, we need introduce two concepts which are \textbf{Factor Bases} and \textbf{Smooth Numbers}.

	A \textbf{Factor Base} is a set of prime factors $S_{fb}=\{p | p \le B\}$ where $B$ is some integer.

	A \textbf{Smooth Number} is an integer in which all its prime factors are within the \textbf{Factor Base} which means if we choose integer $B$ and $Q$, $Q = \prod_{i=1}^k{p_i^{a_i}}$ where $a_i, k \in \mathbb{Z}, p_i \in S_{fb}$. We call Q a \textbf{B-Smooth} Number.

	Recall Kraitchik's Method, he suggests to find a relation $y^2 \equiv \left (\prod_{i=1}^k{x_i}\right)^2 \pmod{n}$. But Dixon's idea is different, he is looking for the relation of $\displaystyle y^2 \equiv Q \equiv \prod_{i=1}^k{p_i^{a_i}} \pmod{n}$ where $a_i \in \mathbb{Z},\ k=|S_{fb}|,\ p_i \in S_{fb}$. For each relation  found, it can be represented as an exponent vector $\vec{v} = \{a_1, a_2, \dots, a_k\}$ over $\mathbb{F}_{2}$. After finding $k$ relations, we have a matrix $m = \{\vec{v_i} | i \le k\}$ and searching the null space of this matrix could help us to find the square integer. Since $M\vec{v} = \vec{0}$ where $\vec{v} \in Null\ Space$, we know which rows sum together are equal to $\vec{0}$, which also implies the products of corresponding Q to that row is a square integer. After we find the relations, let $x^2 = \prod_i^k{Q_i}$, the factor of n is simply $gcd(y\pm x, n)$

	\subsection {Algorithm in Quadratic Sieve}
	Once again, like in previous factoring methods such as in Fermat’s or Dixon’s, we rely on finding two integers, $x$ and $y$,such that N can be expressed as the difference of two squares, $x^{2}-y^{2}$. From there we can apply simply algebra to find the two factors of $N$, $(x-y)$ and $(x+y)$. This may seem simply enough, but how exactly do you find such $x$ and $y$? Surely we could try to check every integer $x$, from $\sqrt{N}$ to $N$ and see if $x^{2}-N$ is a square or not, like in Fermat’s, but this method is too slow for large numbers of $N$, not to mention how you would actually check if $x^{2}-N$ is a perfect square. We, however, don’t need to search the entire interval to find a square. Take for example the number $N = 1649$. The
	$\sqrt{1649} = 41$ so we can begin being to find squares starting with 41.  We have
	$41^{2} - N = 32 = 2^{5}$ \\ $42^{2} - N= 115 = 5\cdot 23$ \\ $42^{3} - N= 200 = 2^{3}\cdot 5^{2}$ mod $N$, and so on.

@@

	So instead of searching through the entire interval from $\sqrt{N}$ to N looking for an individual integer a, such that $a^{2} - N = b^{2}$, we can find a subsequence of integers, such that the product will yield a square as well. But how exactly do you find such a subsequence? Surely we cannot examine all subsequences, for given an interval of length L, there would be $2^{L}$ possible subsequences, in other words, an exponential growth in the number of subsequences as L gets bigger. Furthermore, how long of a sequence do we need to examine before we find such a subsequence, and how do we know what the subsequence is? 

@@

	\\\\LEMMA. If $m_1$,$m_2$,...$m_k$ are positive B-smooth integers, and if $k > \pi(B)$ (where $\pi\left(B\right)$ denotes the number of primes in the interval $[1, B]$), then some non-empty subsequence of ($m_i$) has a product of a square. (Pomerance)

@@

	\\\indent Essentially, Pomerance’s lemma states that if we were to find at least $\pi\left(B\right)$ B-smooth numbers, we are able to find some subsequence of those numbers that would be a product of a square. So say we have a sequence of numbers $m_1$,$m_2$,...$m_k$, where $k>\pi\left(B\right)$, we can represent each $m_i$ as a product of those primes less than $B$, namely $p_1$,$p_2$,...$p_j$. From here we are only interesting in a subsequence of $m_i$’s where there product is a square, but how do we go about finding it? Well, by applying some linear algebra, we can represent each number as an exponent vector of length $j$, the length of our factor base, where each entry in the vector corresponds to the exponent corresponding to the same prime in the prime factorization of $m_i$. For example, given a factor base of \{2,3,5,7\}, the exponent vector of the number 336 would just be [4, 1, 0, 1]. 
	\\\\ Additionally, we want to work with numbers in GF(2), since we are only interested in whether or not some combination will yield even exponents, represented as 0 for even exponent and 1 for odd exponent in our vector, because ultimately we want some subsequence whose product is a square, which means each exponent will be a multiple of 2. After creating such a $k$ by $j$ matrix, we want to find some number of rows who when combined together form a vector of 0's, the zero vector of length $j$, which is why we need to calculate the null space of the matrix. Put simply, the null space of a matrix is the set of all vectors, $v$, such that given a matrix $A$, the product $A\cdot v$, yields the zero vector, which is exactly what we want. In our case the null space will yield vectors, each vector containing only entries of 1s and 0s, in which every 1 corresponds to a row in which that $m_i$ belongs to our subsequence. 
	\\\\You may also ask, how we would populate the factor base given a bound B? Perhaps it may seem necessary to store a large number of primes in order to sieve, but in fact we can easily generate all primes less than B through applying the Sieve of Eratosthenes:

@@

	\\2. Find the next number in the table after p that is not yet crossed off and set p to that number; and then repeat from step 1.
	\\\\Although simple, it is sufficient enough in generating the necessary amount of primes needed. Further implementation details are explained in Sect. 4.5.II Building Factor Base.
	\\\\Now, the problem is, how do we find the necessary amount of B-smooth numbers needed to factor N? Surely, a naive approach would be to trial divide a number by the primes in the factor base until you either get a 1, in which case the number is B-smooth, or you get a number larger larger than B which is not a multiple of any prime in the factor base, in which case it’s not B-smooth. Indeed, this approach would be much too slow, given a sufficiently large bound B, B-smooth numbers are far and few between.
	\\\indent A further improvement could be to only consider numbers which are multiples of primes in the factor base. Say in our interval $[\sqrt{N},N]$ and a prime in our factor base, p, we notice that at some point, x, the number $x^{2}-N$ will be a multiple of p, which can be represented as $\sqrt{N}+i$, where i is the distance from the start of the interval. From there, every subsequent multiple of p is $k*i$ distance away from $\sqrt{N}$. Essentially we will have to solve for $x$ in $x^{2}-N\equiv 0(mod p_i)$, which can yield either 2, 1 or 0 solutions. We can do this for every $p_i$ in the factor base and ‘mark’ numbers that are multiples of said prime. Then, we will only check marked numbers in our interval by dividing only those primes that marked the number, hence not having to check every number in the interval, and not having to trial divide by every prime in the factor base. In the end, this method will work, but does not scale well (as in our case), which is further explained in Sect. 4.5.

@@

	Additionally, with a defined bound B, we must ask ourselves if we should even consider all the primes less than B? Recall the definition of a quadratic residue:

@@

	\\\indent Now the obvious question arises: how do you know if N is a quadratic residue modulo p? Recall the definition of the legendre symbol:

@@

	\[
	\frac{a}{p} = \left\{\begin{array}{lr}
	1, & \textmd{If a is a quadratic residue mod p and a$\not\equiv$ 0$\left(mod p\right)$}\\
	-1, & \textmd{If a is a quadratic non-residue mod p}\\
	0, & \textmd{If $a\equiv 0\left(p\right)$}\\
	\end{array}\right\}
	\]
	\\\\Additionally we will introduce the Law of Quadratic Reciprocity as defined by Gauss:
	\\\\Definition: If p and q are distinct odd primes then:
	\\$\left(\frac{p}{q}\right) = \left(\frac{q}{p}\right)$ if $q\equiv 1(mod 4)$ or $\left(-\frac{q}{p}\right)$ if $q\equiv 3(mod 4)$
	\\This can be restated as $\left(\frac{p}{q}\right)\left(\frac{q}{p}\right) = \left(-1\right)^{\frac{\left((p-1)(q-1)\right)}{4}}$
	\\\\Furthermore, these supplementary properties proved to be useful:
	\\(a)$\frac{1}{p} = 1$
	\\(b)$(\frac{-1}{p}) = (-1)^{\frac{p-1}{2}}$
	\\(c)$(\frac{2}{p}) = (-1)^{\frac{p^{2}-1}{8}})$
	\\(d)$(\frac{a}{p}) \equiv \frac{a(mod p)}{p}$

@@

	From now, we know two ways to test whether $n$ is a quadratic residue mod p, one is Euler's Criterion, and the other is utilizing the Law of Quadratic Reciprocity. In practice, probably because our factor base is not insanely large, we did not notice how much faster the Law of Quadratic Reciprocity was than through Euler's Criterion (since Euler's Criterion is an $\mathcal{O}(\log{n}) $ algorithm).

	\subsubsection{Shanks-Tonelli's Algorithm}

	Shanks-Tonelli's Algorithm is a faster algorithm to find the root of a quadratic residue. In class, we only learned the simple case, which is when $p \equiv 3 \pmod{4}$. Since this algorithm is very important for quadratic sieve, we are going to prove the algorithm.

@@

	Let $p-1 = 2^eS,\ x \equiv n^{\frac{S+1}{2}} \pmod{p},\ t \equiv n^S \pmod{p}.$

	We have, $x^2 \equiv n^{S+1} \equiv n^Sn \equiv tn \pmod{p}$, notice that,

@@

	If $t \not\equiv 1 \pmod{p}$, then find a quadratic non-residue $a$ and let $b \equiv a^S \pmod{p}$, then, $b^{2^e} \equiv (a^S)^{2^e} \equiv a^{2^eS} \equiv a^{p-1} \equiv 1 \pmod{p}$, Since we know $a$ is a quadratic non-residue, By Euler Criterion, $a^{\frac{p-1}{2}} \equiv b^{2^{e-1}} \equiv -1 \pmod{p} \rightarrow 2^e$ is the order of b.

	We have $t^{2^e} \equiv 1 \pmod{p}$, and we let $2^{e^\prime}$ be the order of $t \pmod{p}$, since $n$ is a quadratic residue, $e^\prime \le e-1$

	Let $c \equiv b^{2^{e-e^\prime-1}} \pmod{p}$, $b^\prime \equiv c^2$, $t^\prime = tb^\prime$, $x^\prime = cx$, after this construction, $x^{\prime 2} \equiv t^\prime n \pmod{p}$ still holds, since $x^{\prime 2} \equiv b^{2^{e-e^\prime}}x^2 \equiv tnb^{2^{e-e^\prime}} \equiv tnb^\prime \equiv  t^\prime n \pmod{p}$. Finally, we can repeat this process until $e^\prime = 0$ we can find a $t^\prime = 1$, and our final solution is $ \pm x^\prime \pmod{p}$

@@

	\section {Collecting data by parallel computing} 
	\subsection{Computer spec}
	computer 1: i7-4700M, 2.4GHz (boost 3.1Ghz), RAM 16G\\
	\indent computer 2: i7-3537U, 2.0GHz               , RAM 8G\\
	\indent computer 3: i5-3570K, 3.4GHz               , RAM 16G\\
	\indent computer 4: i5-4210U, 1.7GHz               , RAM 8G
